\begin{defBox}{Finite Product of Sets}[def:15_finite_product]
    Given a finite list of sets \( X_{ 1 } , \ldots , X_{ r } \), we define
    their \textbf{product} to consist of all \( r \)-tuples of the form 
    \( ( x_{ 1 }, x_{ 2 }, \ldots, x_{ r } ) \) where \( x_{ i } \in X_{ i } \)
    for all \( i \). Notationally:
    \begin{equation*}
        \prod_{ i = 1 }^{ r } X_{ i }
        =
        X_{ 1 } \times \ldots \times X_{ r }
        \equiv 
        \left\{
            ( x_{ 1 } , \ldots , x_{ r } )
            \ \middle\vert \ 
            x_{ 1 } \in X_{ 1 } , \ldots , x_{ r } \in X_{ r }
        \right\}
    \end{equation*} 
\end{defBox}

\begin{defBox}{Rectangular Subset}[def:15_rect_subset]
    A \textbf{rectangular subset} is a special kind of subset of a product that 
    has the form:
    \begin{equation*}
        A_{ 1 } \times \ldots \times A_{ r } 
        \subset 
        X_{ 1 } \times \ldots \times X_{ r }
        \quad \mathrm{where} \quad 
        A_{ 1 } \subset X_{ 1 }
        , \ldots , 
        A_{ r } \subset X_{ r }
    \end{equation*}
\end{defBox}

\begin{defBox}{Product Topology}[def:15_product_top]
    Let \( X \) and \( Y \) be topological spaces.
    The \textbf{product topology} on \( X \times Y \) is the topology having as 
    basis the collection \( \mathcal{B} \) of all sets of the form \( U \times
    V \), where \( U \) is an open subset \( X \) and \( V \) is an open subset 
    of \( Y \).
    I.e., we have that a basic open set in the product topology is none other 
    than a product of open sets.

    \baseSkip
    
    We can extend this definition to more than two topological spaces.
    Let \( X_{ 1 } , \ldots , X_{ r } \) be a finite list of topological
    spaces. 
    The collection of all sets of the form: 
    \begin{equation*}
        U_{ 1 } \times \ldots \times U_{ r }
    \end{equation*}
    where we have \( U_{ i } \) to be open in \( X_{ i } \) for all \( i \),
    forms a basis for a topology on \( X_{ 1 } \times \ldots \times X_{ r } \)
    that we call the product topology.
\end{defBox}

\begin{defBox}{Projections}[def:15_projections]
    Let \( \mathrm{proj}_{ 1 } : X \times Y \rightarrow X \) be defined by the 
    equation
    \begin{equation*}
        \mathrm{proj}_{ 1 } ( x, y ) = x
    \end{equation*}
    and let \( \mathrm{proj}_{ 2 } : X \times Y \rightarrow Y \) be defined by 
    the 
    equation
    \begin{equation*}
        \mathrm{proj}_{ 2 } ( x, y ) = y
    \end{equation*}
    The maps \( \mathrm{proj}_{ 1 } \) and \( \mathrm{proj}_{ 2 } \) are called 
    the \textbf{projections} of \( X \times Y \) onto its first and second 
    factors, respectively.

    \baseSkip 

    We can also extend this to more than two topological spaces.
    Let \( X_{ 1 } , \ldots , X_{ r } \) be a finite list of topological
    spaces. 
    Then the projection of \( X_{ 1 } \times \ldots \times X_{ r } \) onto 
    its \( i \)th factor is the map 
    \( \mathrm{proj}_{ i } : X_{ 1 } \times \ldots \times 
    X_{ r } \rightarrow X_{ i } \) defined by the equation
    \begin{equation*}
        \mathrm{proj}_{ i } ( x_{ 1 } , \ldots , x_{ r } ) = x_{ i }
    \end{equation*}
\end{defBox}

\begin{defBox}{Sequences in Products}[def:15_sequence_product]
    If \( X_{ 1 } , \ldots , X_{ r } \) is a product space, then a sequence in
    this space might be written as: \( ( X^{ 0 }, X^{ 1 }, \ldots ) \), where
    \begin{equation*}
        X^{ 0 }
        =
        ( x_{ 1 }^{ 0 } , \ldots , x_{ r }^{ 0 } )
        \quad 
        X^{ 1 }
        =
        ( x_{ 1 }^{ 1 } , \ldots , x_{ r }^{ 1 } )
        \quad 
        \ldots
    \end{equation*}
    are each elements in \( X_{ 1 } , \ldots , X_{ r } \).
\end{defBox}